---
title: "Figure 2"
output:
  html_document:
    toc: true
    code_folding: hide
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
```

This is a side-by-side comparison between figures as they appear in the published work, and the corresponding figures that were re-generated on ` `r date()` `.

```{r}
pipeRoot <- dirname(dirname(getwd()))
# in docker, the $BLJ_PROJ folder is mapped to 'mnt/efs/pipelines'
showPipelineFile <- function(filePath){
    return(gsub(paste0(pipeRoot,"/"), "", filePath))
}
```

The re-produced images are taken from modules under this folder:               
``r gsub("mnt/efs/pipelines/", "<BLJ_PROJ folder>", pipeRoot)``

## Figure2 - Heatmap

```{r out.width=400, out.height=500}
fileName <- "Genus_HeatmapAndCluster.pdf"
dir <- file.path(dir(pipeRoot, full.names = TRUE, pattern = "Heatmap"), "output")
newFile <- file.path(dir, fileName) 
include_graphics(c(fileName, newFile))
```

The left image comes from the publication.  The right image is the pipeline result file:            
``r showPipelineFile(newFile)``


The old and new may not be bit-for-bit identical.  There may some random seed that is used in a training step, or a difference in the font libraries available, graphics paramaters like resolution or image size may be different, the publication may have some manually curated labels that the script-generated image does not.  There are many acceptable reasons why a reproduction of a figure may not be identical to the original; but we expect that the core conclusion from the original will hold for the reproduction.

```{r}
sessionInfo()
```

