---
title: "Review Figures"
author: "Alicia Sorgen and Ivory Blakley"
output:
  pdf_document:
    toc: true
    toc_depth: 3
  html_document:
    toc: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
```

# Review Reproduced Figures

This is a side-by-side comparison between figures as they appear in the published work, and the corresponding figures that were re-generated on:  ` `r date()` `.

The old and new may not be bit-for-bit identical.  There may some random seed that is used in a training step, or a difference in the font libraries available, graphics paramaters like resolution or image size may be different, the publication may have some manually curated labels that the script-generated image does not.  There are many acceptable reasons why a reproduction of a figure may not be identical to the original; but we expect that the core conclusion from the original will hold for the reproduction.

```{r}
pipeRoot <- dirname(dirname(getwd()))
showPipelineRoot <- function(){
    # in docker, the $BLJ_PROJ folder is mapped to 'mnt/efs/pipelines', which is not useful
    return(gsub("/mnt/efs/pipelines", "<BLJ_PROJ folder>", pipeRoot))
}
showPipelineFile <- function(filePath){
    return(gsub(paste0(pipeRoot,"/"), "", filePath))
}
origPanels = getwd()
```

The re-produced images are taken from modules under this folder:               
``r showPipelineRoot()``


\newpage
## Figure 1

```{r Fig1, out.width="100%"}
fig1 = file.path(getwd(), "MainFigure1.png")
include_graphics(fig1)
```

\newpage
### Panel A and B

```{r out.width="50%"}
fileName="Genus_PCO.pdf"
left = file.path(origPanels, fileName)

PCOmodule = dir(pipeRoot, pattern="PCO", full.names=TRUE)
pcoOutDir = file.path(PCOmodule, "output")
right = file.path(pcoOutDir, fileName)

include_graphics(c(left, right))
```

The left image comes from the publication.  The right image is the pipeline result file:            
``r showPipelineFile(right)``

\newpage
### Panel C and D

```{r out.width="50%"}
left = file.path(origPanels, "Genus_scatterPlotsPaper.pdf")

comp16Dir = file.path(dir(pipeRoot, pattern="CompareStudies16S", full.names=TRUE), "output")
right = file.path(comp16Dir, "Genus_mainFigure1cd.pdf")

include_graphics(c(left, right))
```

The left image comes from the publication.  The right image is the pipeline result file:            
``r showPipelineFile(right)``

\newpage
### Panel E

```{r out.width="50%"}
fileName="Genus_coefficientsFromScatterPlots.pdf"
left = file.path(origPanels, fileName)
right = file.path(comp16Dir, fileName)

include_graphics(c(left, right))
```

The left image comes from the publication.  The right image is the pipeline result file:            
``r showPipelineFile(right)``

### Panel F

```{r out.width="50%"}
fileName="Genus_BoxPlotCorrelations.pdf"
left = file.path(origPanels, fileName)
right = file.path(comp16Dir, fileName)

include_graphics(c(left, right))
```

The left image comes from the publication.  The right image is the pipeline result file:            
``r showPipelineFile(right)``


\newpage
## Figure2 

### Heatmap

```{r fig2, out.width="50%"}
fileName <- "Genus_HeatmapAndCluster.pdf"
dir <- file.path(dir(pipeRoot, full.names = TRUE, pattern = "Heatmap"), "output")
newFile <- file.path(dir, fileName) 
include_graphics(c(fileName, newFile))
```

The left image comes from the publication.  The right image is the pipeline result file:            
``r showPipelineFile(newFile)``


\newpage
## Figure 3

```{r Fig3, out.width="100%"}
fig3 = file.path(origPanels, "MainFigure3.png")
include_graphics(fig3)
```

\newpage
### Panels A and B

```{r out.width="80%"}
upper = file.path(origPanels, "Pathway_scatterPlotsMetagenumicsPaper.pdf")

compMeta = file.path(dir(pipeRoot, full.names=TRUE, pattern="_CompareStudiesMetagenomics"),"output")
lower = file.path(compMeta, "Species_mainFigure3ab.pdf")

include_graphics(upper)
include_graphics(lower)
```

The left image comes from the publication.  The lower image is the pipeline result file:            
``r showPipelineFile(lower)``

\newpage
### Panel C

```{r out.width="50%"}
fileName = "Species_coefficientsFromScatterPlots_MetagenomicsBSAndPalleja.pdf"
left = file.path(origPanels, fileName)
right = file.path(compMeta, fileName)

include_graphics(c(left, right))
```

The left image comes from the publication.  The right image is the pipeline result file:            
``r showPipelineFile(right)``

\newpage
### Panels D and E

Upper image is large, scroll down.

```{r out.width="80%"}
upper = file.path(origPanels, "Pathway_scatterPlotsMetagenumicsPaper.pdf")

compPath = file.path(dir(pipeRoot, full.names=TRUE, pattern="CompareStudiesPathways"),"output")
lower = file.path(compPath, "Pathway_mainFigure3de.pdf")

include_graphics(upper)
include_graphics(lower)
```

The left image comes from the publication.  The lower image is the pipeline result file:            
``r showPipelineFile(lower)``

\newpage
### Panel F

```{r out.width="50%"}
fileName = "Pathway_coefficientsFromScatterPlots_MetagenomicsBSAndPalleja.pdf"
left = file.path(origPanels, fileName)
right = file.path(compPath, fileName)

include_graphics(c(left, right))
```

The left image comes from the publication.  The right image is the pipeline result file:            
``r showPipelineFile(right)``


\newpage
## Figure 4

```{r Fig4, out.width="100%"}
fig4 = file.path(getwd(), "MainFigure4.png")
include_graphics(fig4)
```

\newpage
### Panel A 

```{r out.height="30%"}
fileName="performance_heatmap_lasso.png"
upper = file.path(origPanels, fileName)
perform = file.path(dir(pipeRoot, pattern="FigPerformlasso", full.names=TRUE), "output")
lower = file.path(perform, gsub(".png", ".pdf", fileName) )

include_graphics(upper)
include_graphics(lower)
```

The upper image comes from the publication.  The lower image is the pipeline result file:            
``r showPipelineFile(lower)``

\newpage
### Panel B

```{r out.height="30%"}
fileName="loso_performance_lasso.png"
upper = file.path(origPanels, fileName)
lower = file.path(perform, gsub(".png", ".pdf", fileName))

include_graphics(upper)
include_graphics(lower)
```

The upper image comes from the publication.  The lower image is the pipeline result file:            
``r showPipelineFile(lower)``


\newpage
## Figure 5

### All panels

```{r}
fileName="OportunisticPathogens.pdf"

oppPath = file.path(dir(pipeRoot, full.names=TRUE, pattern="OppPathogens"), "output")
lower = file.path(oppPath, fileName)
```

Publication

```{r fig5original}
include_graphics(fileName)
```

Reproduction

```{r fig5Reproduced }
include_graphics(lower)
```

The upper image comes from the publication.  The lower image is the pipeline result file:            
` `r showPipelineFile(lower)` `

\newpage
```{r}
sessionInfo()
```
