---
title: "BioLockJ Reproduced Figures"
author: "Farnaz Fouladi, Alicia Sorgen and Ivory Blakley"
output:
  pdf_document:
    toc: true
    toc_depth: 3
  html_document:
    toc: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
```

\newpage
# Review Reproduced Figures

This is a guidd to help compare figures as they appear in the published work, and the corresponding figures that were re-generated on:                          
` `r date()` `

Supplemental figures that consist of one or two panels are practical to show here.  However, many supplemental documents are multiple pages long, and it is more practical to view the files directly.  The file paths are given here as a guide, but the images are not shown.

The MainFigures.pdf output by the MainFigures module is probably of much greater interest to readers who want to have a side-by-side image comparison.

This document aims to:              

 * Create an easy way for the authors to check that the annotaed figures align with the output of the script, even throughout an iterative review process that may prompt edits at multiple stages of the pipeline.
 * Make the pipeline transparent to readers.
 * Facilitate reproducing the computational components of this work.


```{r}
pipeRoot <- dirname(dirname(getwd()))
showPipelineRoot <- function(){
    # in docker, the $BLJ_PROJ folder is mapped to 'mnt/efs/pipelines'
    return(gsub("/mnt/efs/pipelines", "<BLJ_PROJ folder>", pipeRoot))
}
showPipelineFile <- function(filePath){
    return(gsub(paste0(pipeRoot,"/"), "", filePath))
}
origPanels = getwd()
```

The re-produced images are taken from modules under this folder:               
``r showPipelineRoot()``




```{r include = FALSE}
# library(stringr)
```

\newpage
## Supplemental Figure 1

```{r out.width="50%"}
left = file.path(origPanels, "Diversity.pdf")
diversity = file.path(dir(pipeRoot, pattern="Diversity", full.names=TRUE), "output")
right = file.path(diversity, "Diversity.pdf")

include_graphics(c(left, right))
```

Left (original): ` `r left` `                           
Right (reproduction): ` `r showPipelineFile(right)` ` 


\newpage
## Supplemental Figure 2

Not shown.  Multi-page supplement.

```{r}
compare16s = file.path(dir(pipeRoot, pattern="CompareStudies16S", full.names=TRUE), "output", "Genus_scatterPlots.pdf")
```

To see the reproduction of Supplemental Figure 2, see pipeline file:

` `r showPipelineFile(compare16s)` `


## Supplemental Figure 3

Not shown.  Multi-page supplement.

```{r}
compareSV = file.path(dir(pipeRoot, pattern="CompareStudiesSV", full.names=TRUE), "output", "Seq_scatterPlots.pdf")
```

To see the reproduction of Supplemental Figure 3, see pipeline file:

` `r showPipelineFile(compareSV)` `


\newpage
## Supplemental Figure 4

```{r out.width="50%"}
left = file.path(origPanels, "SV_BS_Assal.pdf")
SVAnalysis = file.path(dir(pipeRoot, pattern="SVAnalysis", full.names=TRUE), "output")
right = file.path(SVAnalysis, "SV_BS_Assal.pdf")

include_graphics(c(left, right))
```

Left (original): ` `r left` `                          
Right(reproduction): ` `r showPipelineFile(right)` ` 

## Supplemental Figure 5

Not shown.  Multi-page supplement.

```{r}
compareMetaGenomics = file.path(dir(pipeRoot, pattern="CompareStudiesMetagenomics", full.names=TRUE), "output", "Species_scatterPlots_MetagenomicsBSAndPalleja.pdf")
```

To see the reproduction of Supplemental Figure 5, see pipeline file:

` `r showPipelineFile(compareMetaGenomics)` `


## Supplemental Figure 6

Not shown.  Multi-page supplement.

```{r}
comparePathway = file.path(dir(pipeRoot, pattern="CompareStudiesPathways", full.names=TRUE), "output", "Pathway_scatterPlots_MetagenomicsBSAndPalleja.pdf")
```

To see the reproduction of Supplemental Figure 6, see pipeline file:

` `r showPipelineFile(comparePathway)` `


\newpage
## Supplemental Figure 7

```{r out.width="50%"}
topleft = file.path(origPanels, "performance_heatmap_randomForest.pdf")
topright = file.path(origPanels, "loso_performance_randomForest.pdf")

forestPerformance = dir(pipeRoot, pattern="FigPerformrandomForest")
includedRandomForest = length(forestPerformance) == 1

if (includedRandomForest){
    lowLeft = file.path(forestPerformance, "output","performance_heatmap_randomForest.pdf")
    lowRight = file.path(forestPerformance, "output","loso_performance_randomForest.pdf")
}else{
    msg="In some iterations of the config file, the random forest training module and the corresponding performance module are commented out to save time in the pipeline.  To include these modules, makes sure the corresponding lines in the config file start with '#BioModule', with exactly 1 '#' character."
    message(msg)
    lowLeft = "When the random forest training module and its performance evaluation module are included, the file will be called: performance_heatmap_randomForest.pdf"
    lowRigth = "When the random forest training module and its performance evaluation module are included, the file will be called: loso_performance_randomForest.pdf"
}

include_graphics(c(topleft, topright))
if (includedRandomForest){ include_graphics(c(lowLeft, lowRigth)) }
```
`r if (!includedRandomForest){msg}`

Top left (original): ` `r topleft` `           
Top right (original): ` `r topright` `     
Lower left (reproduction): ` `r lowLeft` `                           
Lower tight (reproduction): ` `r lowRigth` ` 

\newpage
```{r}
sessionInfo()
```

